---
title: "Developing Data Products Week4 Project"
author: "Sunny Pan"
date: "April 15, 2021"
output: ioslides_presentation
---

<style type="text/css">
body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is the final project in Developing Data Products course. It has two parts: a shiny application and a reproducible pitch presentation. This shiny application will show the effect of vitamin C on tooth growth in Guinea pigs by different supplement dose and supplement delivery methods. 

- The Shiny App: <https://pan-sunny.shinyapps.io/ToothGrowthbyVC/>
- The Source Code:<https://github.com/pan-sunny/DevDataProdProj>

## The Data

This application uses the dataset "ToothGrowth" in RStudio. This dataset stores the length of the teeth growth as a criterion of vitamin C intake of the guinea pig. There are 60 observations and 3 variables:

```{r, eval=TRUE, comment="", echo=TRUE}
head(ToothGrowth)
```

## How it works

1.Choose the plot Data:

- Select the supplement dose level from the dropdown box
- Choose the supplement delivery method in the radio button

2.The ouput figure:

- The bar char will automatically generate accordingly
- The supplement dose will transform from milligram to gram

## The sample plot
*Choose plot data: dose="" and delivery method is "Both"*

```{r, eval=TRUE, message=FALSE, warning=FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
options(scipen = 200)
mydata <- ToothGrowth
vcDose <- ""
vcType <- c("OJ", "VC")
mydata <- mydata %>% filter(supp %in% vcType) %>% group_by(dose, supp) %>% summarise(meanLen = mean(len))
xlab <- "Supplement Vitamin C Dose (milligrams/day)"
ylab <- "ToothGrowth Length"
main <- "The Effect of VitaminC on ToothGrowth in Guinea Pigs"
ggplot(mydata, aes(x=as.factor(dose), y=meanLen, fill=supp))+
        geom_bar(stat = "identity", width=0.5, position = "dodge")+
        labs(x = xlab,y = ylab, title = main)+
        geom_text(aes(label = meanLen),position=position_dodge(width = 0.5),size = 3,vjust = -0.25)
```
